Biases in Planet Occurrence Caused by Unresolved Binaries in Transit Surveys

### 2018-03-01 paper/main.tex
minor conclusion edit
rename figs for aas convention

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{ {\it Top.}---Volumes within which sources appear to be
    searchable for planets of radius $r$.  Single stars are searchable
    out to a distance $d_0$, at which point they become too faint to
    allow the detection of transits.  Binaries are brighter and
    therefore appear to be searchable out to a larger distance.  {\it
    Bottom.}---Volumes within which stars appear to be searchable for
    planets of radius $r/\sqrt{2}$.  }
    \label{fig:model_1_volumes}
\end{figure}

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{ Apparent occurrence rate $\Lambda\a$, and true
    occurrence rate $\Lambda$ in a universe with only one type of
    star, one type of planet (with radius $r$), and $n\b/n\s=0.05$,
    for $n\b$ the number density of binary systems, and $n\s$ the
    number density of single stars.  The occurrence rate of planets
    with radius $r$ is underestimated, and the occurrence rate of
    planets with radius $r/\sqrt{2}$ is overestimated.}
    \label{fig:occ_rate_model_1}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{ The mass ratio distribution of binaries in a
    magnitude-limited sample, assuming the underlying volume-limited
    distribution is uniform and the luminosity-mass relation is
    $L\propto M^{3.5}$. For transit signals of a given amplitude, the
    sample of searchable sources is magnitude-limited, causing high
    mass ratios to be over-represented. }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{ {\it Left.}---Apparent occurrence rate density
      ($\Gamma\a$), compared to the true occurrence rate density
      ($\Gamma_0$) for single stars and primary stars in binaries.
      Three different cases are plotted, with different choices for
      the number of planets per secondary star relative to
      that for single stars ($Z_2/Z_0$).
      {\it Right.}---Same, integrated over $0.5\,R_\oplus$
      bins to give apparent and true occurrence rates.
      In both cases the true planet
      radius distribution is specified by
      Equation~\ref{eq:model3_radius_distribution}.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\subsection{Which star has the planet?}
\label{subsec:whichstar}
\begin{figure}[!t]
    \centering
    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
    \caption{ Fraction of detected planets that orbit single stars
      (solid lines), primary stars of binaries (dashed lines), and
      secondary stars of binaries (dotted lines), as a function of the
      apparent radius of the planet.  We assume that single stars and
      primaries have the same number of planets per star.  Three
      different cases are plotted, differing in the relative
      occurrence of planets around secondary stars ($Z_2/Z_0$).  The
      true radius distribution is given by
      Equation~\ref{eq:model3_radius_distribution}.}
    \label{fig:frac_model_3}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
    \caption{ {\it Left.}---True and apparent occurrence rate densities,
      and {\it right.}---occurrence rates, as a function of planet
      radius, using a model for the radius distribution that exhibits
      a gap between 1.5 and 2\,$R_\oplus$
      (Equation~\ref{eq:model4_radius_distribution}). }
    \label{fig:model_4}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
    \caption{ True and apparent occurrence rate densities, for a
    population of planets with true radii $r$ drawn from a Gaussian
    distribution with mean $14\,R_\oplus$ and standard deviation
    $2\,R_\oplus$.  This is similar to the hot Jupiter distribution
    presented by~\citet{petigura_CKS_2017}.  }
    \label{fig:gaussian_HJ}
\end{figure}

@@

\paragraph{Radius corrections} Another application of our formalism is
to help in those cases in which it is not clear whether the primary or
secondary star is the source of a transit signal.  By this point
almost all of the {\it Kepler}\ Objects of Interest have been examined
with high resolution imaging~\citep{
  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been summarized
by~\citet{furlan_kepler_2017}. Based on this information,
\citet{hirsch_assessing_2017} re-assessed the radius measurements of
the {\it Kepler} planets in binaries. They found that planet radii are
generally underestimated by a factor $r/r\a = 1.17$ if all planets
orbit primaries, and $r/r\a = 1.65$ if detected planets are equally
likely to orbit primaries and singles.  Our formalism provides a way
to assess the relative probabilities that a detected planet orbits the
primary or secondary star.  The calculations presented in
\S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
most likely orbits the primary star.

>>>>

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/f1.pdf}
    \end{center}
    \caption{ {\it Top.}---Volumes within which sources appear to be
    searchable for planets of radius $r$.  Single stars are searchable
    out to a distance $d_0$, at which point they become too faint to
    allow the detection of transits.  Binaries are brighter and
    therefore appear to be searchable out to a larger distance.  {\it
    Bottom.}---Volumes within which stars appear to be searchable for
    planets of radius $r/\sqrt{2}$.  }
    \label{fig:model_1_volumes}
\end{figure}

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/f2.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{ Apparent occurrence rate $\Lambda\a$, and true
    occurrence rate $\Lambda$ in a universe with only one type of
    star, one type of planet (with radius $r$), and $n\b/n\s=0.05$,
    for $n\b$ the number density of binary systems, and $n\s$ the
    number density of single stars.  The occurrence rate of planets
    with radius $r$ is underestimated, and the occurrence rate of
    planets with radius $r/\sqrt{2}$ is overestimated.}
    \label{fig:occ_rate_model_1}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/f3.pdf}
    \caption{ The mass ratio distribution of binaries in a
    magnitude-limited sample, assuming the underlying volume-limited
    distribution is uniform and the luminosity-mass relation is
    $L\propto M^{3.5}$. For transit signals of a given amplitude, the
    sample of searchable sources is magnitude-limited, causing high
    mass ratios to be over-represented. }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/f4a.pdf}{figures/f4b.pdf}
    \caption{ {\it Left.}---Apparent occurrence rate density
      ($\Gamma\a$), compared to the true occurrence rate density
      ($\Gamma_0$) for single stars and primary stars in binaries.
      Three different cases are plotted, with different choices for
      the number of planets per secondary star relative to
      that for single stars ($Z_2/Z_0$).
      {\it Right.}---Same, integrated over $0.5\,R_\oplus$
      bins to give apparent and true occurrence rates.
      In both cases the true planet
      radius distribution is specified by
      Equation~\ref{eq:model3_radius_distribution}.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\subsection{Which star has the planet?}
\label{subsec:whichstar}
\begin{figure}[!t]
    \centering
    \includegraphics[width=\textwidth]{figures/f5.pdf}
    \caption{ Fraction of detected planets that orbit single stars
      (solid lines), primary stars of binaries (dashed lines), and
      secondary stars of binaries (dotted lines), as a function of the
      apparent radius of the planet.  We assume that single stars and
      primaries have the same number of planets per star.  Three
      different cases are plotted, differing in the relative
      occurrence of planets around secondary stars ($Z_2/Z_0$).  The
      true radius distribution is given by
      Equation~\ref{eq:model3_radius_distribution}.}
    \label{fig:frac_model_3}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/f6a.pdf}{figures/f6b.pdf}
    \caption{ {\it Left.}---True and apparent occurrence rate densities,
      and {\it right.}---occurrence rates, as a function of planet
      radius, using a model for the radius distribution that exhibits
      a gap between 1.5 and 2\,$R_\oplus$
      (Equation~\ref{eq:model4_radius_distribution}). }
    \label{fig:model_4}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/f7.pdf}
    \caption{ True and apparent occurrence rate densities, for a
    population of planets with true radii $r$ drawn from a Gaussian
    distribution with mean $14\,R_\oplus$ and standard deviation
    $2\,R_\oplus$.  This is similar to the hot Jupiter distribution
    presented by~\citet{petigura_CKS_2017}.  }
    \label{fig:gaussian_HJ}
\end{figure}

@@

\paragraph{Radius corrections} Another application of our formalism is
to help in those cases in which it is not clear whether the primary or
secondary star is the source of a transit signal.  By this point
almost all of the {\it Kepler}\ Objects of Interest have been examined
with high resolution imaging~\citep{
  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been summarized
by~\citet{furlan_kepler_2017}. Based on this information,
\citet{hirsch_assessing_2017} re-assessed the radius measurements of
the {\it Kepler} planets in binaries. They found that planet radii are
generally underestimated by a factor $r/r\a = 1.17$ if all planets
orbit primaries, and $r/r\a = 1.65$ if detected planets are equally
likely to orbit primaries and singles.  Our formalism provides a way
to assess the relative probabilities that a detected planet orbits the
primary or secondary star.  The calculations presented in
\S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
most likely orbits the primary star.  Additionally, the fraction of
detected planets that are actually in unresolved binaries should
increase towards smaller apparent radii.
